### 2017-07-02 paper/synthesis.tex
finished the algorithmic section

Both soundness and relative completeness of Algorithm~\ref{algo:linlexrsm} follow by arguments identical to those presented in~\cite{xxx}. 
\begin{theorem}
	Suppose that Algorithm~\ref{algo:linlexrsm} is run on an \APP{} $\program$ together with linear invariant map $\inv$. If teh algorithm returns a $d$-dimensional LEM $\vec{\lem}=(\lem_1,\dots,\lem_d)$, then $\vec{\lem}$ is a $1$-LinLexRSM map for $\program$ supported by $\inv$. Conversely, if the algorithm returns ``No LinLexRSM'', then for any $d'\in \Nset$ and $\eps>0$ there is no $d'$-dimensional $\eps$-LinLexRSM for $\program$  supported by $\inv$.
\end{theorem}
\begin{proof}[Proof (sketch)]
For soundness, let $U_i$ and $U_{i}$ denote the content of $U$ just before the $i$-th iteration of the while loop. Then each $\tilde{\tau}\in U_{i}\setminus U_{i+1}$ is $1$-ranked by $\lem_i$, for each $1\leq i \leq d$. Since $U_{d}=\emptyset$, each generalized transition of $\pCFG_{\program}$ is 1-ranked by some component of $\vec{\lem}$. Since \textbf{[PETR: REWRITE (1) TO REQUIRE NON-NEG EVERYWHERE]}
\end{proof}

>>>>

Both soundness and relative completeness of Algorithm~\ref{algo:linlexrsm} follow by arguments identical to those presented in~\cite{xxx}. 
\begin{theorem}
	Suppose that Algorithm~\ref{algo:linlexrsm} is run on an \APP{} $\program$ together with linear invariant map $\inv$. If teh algorithm returns a $d$-dimensional LEM $\vec{\lem}=(\lem_1,\dots,\lem_d)$, then $\vec{\lem}$ is a $1$-LinLexRSM map for $\program$ supported by $\inv$. Conversely, if the algorithm returns ``No LinLexRSM'', then for any $d'\in \Nset$ and $\eps>0$ there is no $d'$-dimensional $\eps$-LinLexRSM for $\program$  supported by $\inv$.
\end{theorem}
\begin{proof}[Proof (sketch)]
For soundness, let $U_i$ and $U_{i}$ denote the content of $U$ just before the $i$-th iteration of the while loop. Then each $\tilde{\tau}\in U_{i}\setminus U_{i+1}$ is $1$-ranked by $\lem_i$, for each $1\leq i \leq d$. Since $U_{d}=\emptyset$, each generalized transition of $\pCFG_{\program}$ is 1-ranked by some component of $\vec{\lem}$. Non-negativity of each $\lem_i$ is ensured directly by $\lp_{U_i}$. Hence, it remains to show that each $\tilde{\tau}\in U_i$ is unaffected by $\lem_1,\dots,\lem_{i-1}$. But this follows from $U_i \subseteq U_{i-1}\subseteq \cdots\subseteq U_1$ and from the fact that each gen. transition in $U_j$ is unaffected by $\lem_j$.

Proving completeness is more intricate; as pointed out in~\cite{xxx}, one needs to show that the greedy strategy of selecting LEM that ranks maximal number of remaining transitions does not cut off some possible LinLexRSMs. In~\cite{xxx} the completeness of the greedy strategy is proved by using several geometric arguments that exploit the fact that the underlying programs are affine. The same geometric properties hold for our \APP{}s (all ranking conditions in Definitions~\ref{def:rank1} and~\ref{def:rank2} are linear in program variables), the result is easily transferable.
\end{proof}
